A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Oh so purdy

The algorithm builds up a mapping $M$, starting with the empty mapping
$\emptyset$ and adding a $(v_i, w_i)$ pair at each level of the search tree.
Select a vertex in $\V(\graphG)$ as the first vertex to be mapped; in our
example we will arbitrarily choose vertex $1$. Each of the vertices in
$\V(\graphH)$ to which vertex $1$ may be mapped will be tried in turn, and
finally the possibility where vertex $1$ remains unmatched will be tried.

@@

\begin{figure}[htb]
\centering
% Bipartite graph TikZ based on code from
% https://tex.stackexchange.com/a/15094/61367
\definecolor{myblue}{RGB}{240,240,240}
\definecolor{mygreen}{RGB}{120,120,120}
\usetikzlibrary{positioning,chains,fit,shapes,calc}

@@

\caption{A bipartite graph of the type used to calculate a bound in CP-FC}
\label{fig:cpfc-bipartite}
\end{figure}

>>>>

The algorithm builds up a mapping $M$ using a depth-first search, starting with the empty mapping
$\emptyset$ and adding a $(v_i, w_i)$ pair at each level of the search tree.
Select a vertex in $\V(\graphG)$ as the first vertex to be mapped; in our
example we will arbitrarily choose vertex $1$. Each of the vertices in
$\V(\graphH)$ to which vertex $1$ may be mapped will be tried in turn, and
finally the possibility where vertex $1$ remains unmatched will be tried.

@@

\begin{figure}[htb]
\centering
% Bipartite graph TikZ based on code from
% https://tex.stackexchange.com/a/15094/61367
\definecolor{myblue}{RGB}{79.0, 18.0, 123.0}
\definecolor{mygreen}{RGB}{251.0, 135.0, 97.0}
\usetikzlibrary{positioning,chains,fit,shapes,calc}

@@

\caption{A bipartite compatibility graph of the type used to calculate a bound in the CP-FC algorithm.}
\label{fig:cpfc-bipartite}
\end{figure}
